---
# title: "Tutorial"
# author: "Maryam Seifeldin"
# date: "11/4/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(ltm)
library(car)
library(gmodels)

choice_data <- read.csv("ExampleData_choice.csv", header=TRUE)
numeric_data <- read.csv("ExampleData_numeric.csv", header=TRUE)
numeric_data <- subset(numeric_data, Consent==1)
choice_data <- subset(choice_data, Consent=="Yes")
choice_data <- choice_data[, -c(1:17)]
numeric_data <- numeric_data[, -c(1:17)]
numeric_data$SDO1R <- recode(numeric_data$SDO1,"1=7; 2=6; 3=5; 4=4; 5=3; 6=2; 7=1; else=NA")
numeric_data$SDO2R <- recode(numeric_data$SDO2,"1=7; 2=6; 3=5; 4=4; 5=3; 6=2; 7=1; else=NA")
numeric_data$SDO5R <- recode(numeric_data$SDO5,"1=7; 2=6; 3=5; 4=4; 5=3; 6=2; 7=1; else=NA")
numeric_data$SDO6R <- recode(numeric_data$SDO6,"1=7; 2=6; 3=5; 4=4; 5=3; 6=2; 7=1; else=NA")
SDO <- data.frame(numeric_data$SDO1R, numeric_data$SDO2R, 
                  numeric_data$SDO3, numeric_data$SDO4, 
                  numeric_data$SDO5R, numeric_data$SDO6R,
                  numeric_data$SDO7, numeric_data$SDO8)
SDO <- mutate_all(SDO, function(x) as.numeric(as.character(x)))
SDO$SDO_mean_scores <- rowMeans(SDO, na.rm = TRUE)
analysis_data <- data.frame(choice_data$GEND, numeric_data$AGE, choice_data$condition, choice_data$PPP1, SDO$SDO_mean_scores)
names(analysis_data) <- c("Gender", "Age", "Condition","PoliticalParty", "SocialDominance")
analysis_data$Age <- as.numeric(as.character(analysis_data$Age))
```
Here, we'll test whether there's a statistically significant difference between the conditions in social dominance orientation:
```{r, eval = TRUE} 
Condition_x_SocialDominance <- aov(SocialDominance ~ Condition, na.action=na.exclude, data= analysis_data)
summary(Condition_x_SocialDominance)
```
To report an ANOVA properly, you'll need the p-value (Pr(>F)), the F-value, the between-groups degrees of freedom (Df x Independent Variable -- here, it's Condition), and the within-groups degrees of freedom (Df x Residuals) You'll also need the grouped means and the grouped standard deviations (which you'll need to calculate yourself; see descriptive statistics page).

If you get a statistically significant result, you should also run a Tukey post-hoc analysis:
```{r, eval = TRUE} 
Condition_x_SocialDominance_Tukey <- TukeyHSD(Condition_x_SocialDominance)
Condition_x_SocialDominance_Tukey
```
You won't need to report any of these numbers, but you will need to report which condition comparisons get statistically significant results.