---
# title: "Tutorial"
# author: "Maryam Seifeldin"
# date: "11/4/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(ltm)
library(car)
library(fastDummies)

valdata <- read.csv("altruism_data_values.csv", header=TRUE)
numdata <- read.csv("altruism_data_numeric.csv", header=TRUE)
fulldata <- numdata
ourdata <- subset(fulldata, Consent==1)
data <- dplyr::select(ourdata,.data$praise_rejection_1 : .data$botcatcher)
colnames(data)[19] <- "Age"
data[,] <- sapply(data[,], as.character)
data$condition <- ifelse(data$likely_nonpro != "", "nonpro", "pro")
data$vignette_response <- ifelse(data$likely_nonpro == "", data$likely_pro, data$likely_nonpro)
data$justification <- ifelse(data$bot_catcher == "", data$botcatcher, data$bot_catcher)
data <- subset(data, select = -c(likely_nonpro, likely_pro, botcatcher, bot_catcher))
data$vignette_response <- as.numeric(data$vignette_response)
data$Age <- as.numeric(data$Age)
data[,1:18] <- sapply(data[,1:18],as.numeric)
data <- data %>%
  mutate(justification,
         praise_rejection = rowMeans(dplyr::select(., -c(Age, condition, vignette_response, justification)),na.rm = TRUE))

```
First we look at the Age column and note the minimum and maximum of the data values. We note there is nobody under the age of 20, and nobody over the age of 59 in our dataset.  
So here we use an embedded ifelse() statement to separate our raw age data into bins, or brackets:
```{r, eval = TRUE} 
data$age_bracket <- ifelse(data$Age < 30 , "20s" , 
                           ifelse(data$Age < 40 , "30s", 
                                  ifelse(data$Age < 50 , "40s", "50s")))
```
Code translation: we make a new column called age_bracket and tell R to go through each row of data in the Age column and evaluate it by the ifelse() statement to generate a value for the age_bracket column. First, if the value is less than 30, we assign the cell a character string value of "20s". If it isn't less than 30, it checks if the value is less than 40. If it is, we assign the cell a character string value of "30s". If it isn't less than 40, it checks if the value is less than 50. If it is, we assign the cell a character string value of "40s". If it isn't less than 50, we assign the cell a character string value of "50s".   