---
# title: "Tutorial"
# author: "Maryam Seifeldin"
# date: "11/4/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(ltm)
library(car)
library(gmodels)

choice_data <- read.csv("ExampleData_choice.csv", header=TRUE)
numeric_data <- read.csv("ExampleData_numeric.csv", header=TRUE)
numeric_data <- subset(numeric_data, Consent==1)
choice_data <- subset(choice_data, Consent=="Yes")
choice_data <- choice_data[, -c(1:17)]
numeric_data <- numeric_data[, -c(1:17)]
numeric_data$SDO1R <- recode(numeric_data$SDO1,"1=7; 2=6; 3=5; 4=4; 5=3; 6=2; 7=1; else=NA")
numeric_data$SDO2R <- recode(numeric_data$SDO2,"1=7; 2=6; 3=5; 4=4; 5=3; 6=2; 7=1; else=NA")
numeric_data$SDO5R <- recode(numeric_data$SDO5,"1=7; 2=6; 3=5; 4=4; 5=3; 6=2; 7=1; else=NA")
numeric_data$SDO6R <- recode(numeric_data$SDO6,"1=7; 2=6; 3=5; 4=4; 5=3; 6=2; 7=1; else=NA")
SDO <- data.frame(numeric_data$SDO1R, numeric_data$SDO2R, 
                  numeric_data$SDO3, numeric_data$SDO4, 
                  numeric_data$SDO5R, numeric_data$SDO6R,
                  numeric_data$SDO7, numeric_data$SDO8)
```
If you have a Likert scale that you've already reverse coded as per the instructions above, you should have a dataframe with just the columns of raw scores for that scale. Using our example data, we run the following command to make a new column in that dataframe called SDO_mean_scores, where each row in the column contains the mean of all the other cells in the same row of the dataframe:
```{r, eval = TRUE, include=FALSE}
SDO <- mutate_all(SDO, function(x) as.numeric(as.character(x)))
```
```{r, eval = TRUE}
SDO$SDO_mean_scores <- rowMeans(SDO, na.rm = TRUE)
```
*If you get an error similar to "Error in rowMeans(SDO, na.rm = TRUE) : 'x' must be numeric", run the following code on your variable dataframe, then try the mean score calculation again:
```{r, eval = TRUE}
SDO <- mutate_all(SDO, function(x) as.numeric(as.character(x)))
```