---
# title: "Tutorial"
# author: "Maryam Seifeldin"
# date: "11/4/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(ltm)
library(car)
library(gmodels)

choice_data <- read.csv("ExampleData_choice.csv", header=TRUE)
numeric_data <- read.csv("ExampleData_numeric.csv", header=TRUE)
numeric_data <- subset(numeric_data, Consent==1)
choice_data <- subset(choice_data, Consent=="Yes")
choice_data <- choice_data[, -c(1:17)]
numeric_data <- numeric_data[, -c(1:17)]
```
Here we create a new column in our dataframe called "SDO1R" and tell R to take the SDO1 column and fill our new column with recoded data as we have specified in the quotes inside the recode() function.
```{r, eval = TRUE}
numeric_data$SDO1R <- recode(numeric_data$SDO1, "1=7; 2=6; 3=5; 4=4; 5=3; 6=2; 7=1; else=NA")
```
compare the contents of the SDO1 column:
```{r, eval = TRUE}
numeric_data$SDO1
```
to the contents of the reversed column:
```{r, eval = TRUE}
numeric_data$SDO1R
```
It worked! So, we repeat the process with each of the columns that need reverse coding:
```{r, eval = TRUE}
numeric_data$SDO2R <- recode(numeric_data$SDO2,"1=7; 2=6; 3=5; 4=4; 5=3; 6=2; 7=1; else=NA")
numeric_data$SDO5R <- recode(numeric_data$SDO5,"1=7; 2=6; 3=5; 4=4; 5=3; 6=2; 7=1; else=NA")
numeric_data$SDO6R <- recode(numeric_data$SDO6,"1=7; 2=6; 3=5; 4=4; 5=3; 6=2; 7=1; else=NA")
```
Now, in order to analyze this variable properly and effectively, we collect all the reversed columns and all the original versions of the non-reversed columns into a single data frame:
```{r, eval = TRUE}
SDO <- data.frame(numeric_data$SDO1R, numeric_data$SDO2R, 
                  numeric_data$SDO3, numeric_data$SDO4, 
                  numeric_data$SDO5R, numeric_data$SDO6R,
                  numeric_data$SDO7, numeric_data$SDO8)
```
With this dataframe, we can calculate both Cronbach's Alpha and the mean scores for this scale.