---
# title: "Tutorial"
# author: "Maryam Seifeldin"
# date: "11/4/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(ltm)
library(car)

valdata <- read.csv("altruism_data_values.csv", header=TRUE)
numdata <- read.csv("altruism_data_numeric.csv", header=TRUE)
fulldata <- numdata
ourdata <- subset(fulldata, Consent==1)
data <- dplyr::select(ourdata,.data$praise_rejection_1 : .data$botcatcher)
colnames(data)[19] <- "Age"
data[,] <- sapply(data[,], as.character)
data$condition <- ifelse(data$likely_nonpro != "", "nonpro", "pro")
data$vignette_response <- ifelse(data$likely_nonpro == "", data$likely_pro, data$likely_nonpro)
data$justification <- ifelse(data$bot_catcher == "", data$botcatcher, data$bot_catcher)
```
Here we create a new column in our dataframe called "reversed" and tell R to take the praise_rejection_1 column and fill our new column with recoded data as we have specified in the quotes inside the recode() function.
```{r, eval = TRUE}
data$reversed <- recode(data$praise_rejection_1, "1=7; 2=6; 3=5; 4=4; 5=3; 6=2; 7=1;")
```
compare the contents of the praise_rejection_1 column:
```{r, eval = TRUE}
data$praise_rejection_1
```
to the contents of the reversed column:
```{r, eval = TRUE}
data$reversed
```
Now, to have the "reversed" data replace the data in the original column, we delete the original column and rename the reversed column with the name of the original column:
```{r, eval = TRUE}
data$praise_rejection_1 <- NULL
data <- rename(data, praise_rejection_1 = reversed)
```